Self-test prime dimensional EPR pairs with constant alphabet

### 2019-01-31 Draft/draft.tex
Honghao: new proof of Prop.12, constructed isometries for Thm. 15, and other editorial changes

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{EPR^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\G}{G}
\newcommand{\LS}{LS}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}

@@

In summary, general $d$-dimensional maximally entangled states are self-tested by
modifying the correlation and enlarging the size of the correlation.
A natural question to ask is whether maximally entangled state with large local dimension
can be self-tested with fixed-sized correlation. 
An equivalent question to ask is whether it is possible to self-test maximally
entangled state more efficiently, with constant question and answer set. 
In this report, we give an affirmative answer to this question by proving the following theorem.
\begin{theorem}
\label{thm:inf}
	There exists an infinite-sized set $D$ of odd prime numbers such that, for any $d \in D$, 
	the maximally entangled state of local dimension $d-1$ can be self-tested 
	with constant-sized question and answer alphabets.
\end{theorem}

The set $D$ is easily characterizable as it contains all the odd prime numbers with 
primitive root $2$, $3$ or $5$. It has been shown that there are infinitely many prime numbers
with primitive root in the set $\{2,3,5\}$ \cite{murty1988}, so the set $D$ has infinitely many elements.
To prove \cref{thm:inf}, we give explicit self-testing proof of 
the maximally entangled state with local dimension $d-1$ where the primitive root of $d$ is $2$ by explicitly giving the 
correlation that achieves this goal. Then the self-testing property of this correlation is 
given in the following theorem.
\begin{theorem}
\label{thm:pr_2}
	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
	primitive root $2$, can be self-tested by a constant-sized correlation.
\end{theorem}
Note that although the sizes of the question and answer
sets do not depend on $d$, the optimal correlation does.
This correlation can be easily converted to work for dimensions with primitive $3$ or $5$.

@@

\textbf{The weighted CHSH inequality \cite{acin2012}.}
The first building-block of our result is a robust self-testing result based on the weighted CHSH inequality.
In the CHSH scenario, Alice and Bob has binary observables $A_x,B_y$ for $x,y = 0,1$ 
on Hilbert space $\calH_A$ and $\calH_B$ respectively.
A binary observable is a Hermitian matrix whose eigenvalues are either $+1$ or $-1$.
The weighted CHSH inequality is given by 
\begin{align}
	\label{eq:chsh_op}
	\I_\alpha = \alpha\ip{A_0B_0}+\alpha\ip{A_0B_1} + \ip{A_1B_0} - \ip{A_1B_1}\leq 2\alpha,
\end{align}
where $\ip{A_xB_y}$ is the expectation value of of the observables.
If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, they cannot violate
the weighted CHSH inequality.
However, If they share entangled state $\ket{\psi}$, the maximal violation is 
\begin{align}
\label{eq:chsh_max}
 \I_\alpha \leq 2\sqrt{1+\alpha^2}.
\end{align}
\begin{definition}[Ideal strategy for $\I_\alpha$]
	\label{def:ideal}
	Define $\mu = \arctan(1/\alpha)$.
	The ideal strategy for weighted CHSH with parameter $\alpha$ (i.e. achieving maximal violation in \cref{eq:chsh_max})
	consists of the joint state $\ket{\EPR{2}}$ and observables $A_0 = \pauliz$, $A_1 = \paulix$,
	$B_0 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $B_1 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
\end{definition}
An interesting observation of the weighted CHSH inequality is that its maximal violation can certify the shared states and the 
measurements, which is the phenomenon of self-test. We give formal statement of this self-test result in \cref{sec:chsh}.

@@

%=======================================
\section{The linear system game}
\label{sec:lsg}
%=======================================
The goal of this section and the following two sections is to 
present a correlation that can self-test $\ket{\EPR{d-1}}$, 
where $d$ is prime and has primitive root $2$. 
The correlation we constructed is the optimal correlation for a game $\G$, which is the combination of two tests.
In this section, we introduce the linear system game which tests a relation that should be satisfied by 
Alice and Bob's observables.

Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$.
The main component of $\G$ is a linear system game $\LS$, whose solution group is the embedding of the 
following group
\begin{align}
	\Pg= \langle u, x : uxu^{-1} = x^2 \rangle.
\end{align}
In other words, relations in the presentation of the solution group of $\LS$ can be combined to derive the
relation $uxu^{-1} = x^2$.
\begin{proposition}
	\label{prop:embed}
	The group $\Pg$ can be embedded into a linear system game $\LS$ over $\Z_2$,
	with $118$ variables and $91$ equations, where each equation involves $3$ variables.
\end{proposition}
The process of embedding $\Pg$ into the solution group of $\LS$ follows the recipe given in the proofs of
Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Slofstra's seminal work \cite{slofstra2017}.
The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}.
We give details of this embedding process in \cref{sec:power2}.

In the later parts of the paper, we use $n = 118$ and $m = 91$ to refer to the size of $\LS$.
The key feature of this embedding is that $\LS$ has constant-sized input-output alphabet
even if the generators $u$ and $x$ can have arbitrary order. 
We denote the special operators in the operator solution of $\LS$ that correpsond to generators 
$u = x_3x_4$ and $x = x_1x_2$ by $U$ and $X$.
The key relation that we will use in the later section is that 
\begin{align}
	(A_3A_4) (A_1A_2)(A_4A_3) \ket{\psi} = (A_1A_2)^2\ket{\psi}, 
\end{align}
where $\ket{\psi}$ is the state shared between Alice and Bob and $A_i$ is 
Alice's observable for $1 \leq i \leq n$.

The special property of $U$ and $X$ is summarized in the following lemma. 
\begin{lemma}
	\label{lm:ux_independ}
	Suppose there exist unitaries $U$ and $X$ which have the following forms
	\begin{align}
		X = \sum_{i=1}^{d-1} \omega_d^i \ketbra{i}{i} && U = \sum_{i=1}^{d-1}\ketbra{i/2}{i},
	\end{align}
	then the set $\{U^k X^l\}$ for $k=0,1\dots d-2$ and $l = 1,2\dots d-1$ forms a basis of 
	the ring of $(d-1)\times (d-1)$ matrices over $\C$.
\end{lemma}
Note that the unitaries $U$ and $X$ defined in the lemma above satisfy the condition $UXU^\dagger = X^2$.
In the self-test proof, this lemma will be a critical step.
\begin{proof}
We are going to show the $(d-1)^2$ matrices from the set $\{U^k X^l\}_{k \in[d-1], l \in [d-1]+1}$ are linearly independent.
Suppose there exists a set of complex numbers $\{ x_{k,l} \}_{k \in[d-1], l \in [d-1]+1}$
such that 
\begin{align}
	M = \sum_{k=0}^{d-2} \sum_{l=1}^{d-1} x_{k,l} U^k X^l = 0. 
\end{align}
We further assume that there exists a set of integers $\{ k_i \}_{i=1}^{d-1}$ such that $2^{k_i} \equiv i \pmod{d}$.
The fact that $2$ is a primitive root of $d$ guarantees that $k_i$'s are distinct.
Then we can group $\{x_{k,l}\}$ into vectors: $\ket{x_{k_1}}, \ket{x_{k_2}} \dots \ket{x_{k_{d-1}}}$,
where $\ket{x_{k_i}}= (x_{k_i, 1}, x_{k_i, 2} \dots x_{k_i, d-1})^\intercal$.
Our goal is equivalent to proving that $\ket{x_{k_i}} = 0$ for all $i$.

@@

%======================================
\section{The extended weighted CHSH test}
\label{sec:chsh}
%======================================
Before introducing the extended weighted CHSH test, we fill in some background about the weighted CHSH inequality,
namely, that its maximal violation can self-test $2$-dimensional EPR pair and rotated Pauli operators.
The robust self-testing result is summarized in the following theorem.
\begin{theorem}
\label{thm:selftest}
	Suppose the quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the violation
	at least $2\sqrt{1+\alpha^2} - \epsilon$
	for some $\epsilon$, then
	there exists a local isometry $\Phi = \Phi_A \x \Phi_B$ and an auxiliary state $\ket{aux}$  such that
	\begin{align}
		\| \Phi( \tilde{A}_x \x \tilde{B}_y \ket{\psi}) -\ket{aux} \x (A_x \x B_y) \ket{\EPR{2}}  \| = O(\sqrt{\epsilon})
	\end{align}
	for $x,y \in \{-1, 0, 1\}$ where the subscript $-1$ refers to the identity operator and $A_x, B_y$ are 
	defined in \cref{def:ideal}. \hl{Error term depend on $\alpha$.}
\end{theorem}
Our approach is very similar to the one used in Ref.~\cite{bamps2015} so we 
defer the proof of \cref{thm:selftest} till \cref{sec:selftest}.
After proving the robust self-testing result, we take one step further and observe an interesting property of the 
product of Bob's observables.
\begin{proposition}
\label{prop:2d-subspace}
	Suppose a quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the maximal 
	violation of  $\I_{\cot(-\pi/2d)}$, then $\supp(\Tr_A(\ketbra{\psi}{\psi}))$ is spanned by $\omega_d$-eigenvectors 
	and $\omega_d^{-1}$ -eigenvectors of $\tilde{B}_0\tilde{B}_1$.
\end{proposition}
\begin{proof}[Proof of \cref{prop:2d-subspace}]
	By \cref{thm:selftest}, the condition that the strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]}, \{\tilde{B}_y\}_{y \in [2]})$ achieves the  
	maximal value of $\I_{\cot(-\pi/2d)} $ implies that 
	\begin{align}
		\ket{\tpsi} = \sum_{i=1}^m \frac{c_i}{\sqrt{2}} (\ket{u_{i,0}}\ket{u_{i,0}}+\ket{u_{i,1}}\ket{u_{i,1}}),
	\end{align}
	where $c_i$'s are coefficients such that $\sum_{i=1}^m \norm{c_i}^2 = 1$.
	The special property of the subspace $V_i = \spn( \ket{u_{i,0}}, \ket{u_{i,1}})$ is that 
	\begin{align*}
	(\tilde{B}_0 + \tilde{B}_1) \ket{u_{i,0}} = 2\cos(-\pi/2d) \ket{u_{i,0}} 
	&&(\tilde{B}_0 + \tilde{B}_1) \ket{u_{i,1}} = -2\cos(-\pi/2d) \ket{u_{i,1}}\\
	(\tilde{B}_0 - \tilde{B}_1) \ket{u_{i,0}} = 2\sin(-\pi/2d) \ket{u_{i,1}} 
	&&(\tilde{B}_0 - \tilde{B}_1) \ket{u_{i,1}} = 2\sin(-\pi/2d) \ket{u_{i,0}}.
	\end{align*}
	It is straightforward to calculate that 
	\begin{align*}
		\tilde{B}_0\tilde{B}_1 \ket{u_{i,0}} = \cos(\pi/d) \ket{u_{i,0}} -\sin(\pi/d) \ket{u_{i,1}},&&
		\tilde{B}_0\tilde{B}_1\ket{u_{i,1}} = \sin(\pi/d)\ket{u_{i,0}} + \cos(\pi/d) \ket{u_{i,1}},
	\end{align*}
	so we can conclude that 
	\begin{align*}
		&\tilde{B}_0\tilde{B}_1(\ket{u_{i,0}} + i\ket{u_{i,1}}) = e^{i \frac{\pi}{d}} (\ket{u_{i,0}} + i\ket{u_{i,1}}), &&
		&\tilde{B}_0\tilde{B}_1(\ket{u_{i,0}} - i\ket{u_{i,1}}) = e^{-i \frac{\pi}{d}} (\ket{u_{i,0}} - i\ket{u_{i,1}}).
	\end{align*}
	Hence each $V_i$ is spanned by $\omega_d$-eigenvector and $\omega_d^{-1}$-eigenvector of $\tB_0\tB_1$.
\end{proof}
Suppose the subspace $V = \spn(\ket{u_0}, \ket{u_1})$, then
the actual eigenbasis of $X = B_0B_1$ that we use is 
\begin{align}
	\ket{x_1} = \frac{-1}{\sqrt{2}}(\ket{u_0} + i\ket{u_1}), &&
	\ket{x_{d-1}} = \frac{-e^{i\pi/2d}}{\sqrt{2}}(\ket{u_0} - i\ket{u_1}),
\end{align}
such that 
\begin{align}
	&B_0 = \omega_d\ketbra{x_1}{x_{d-1}} + \omega_d^{-1} \ketbra{x_{d-1}}{x_1},\\
	&B_1 =\ketbra{x_1}{x_{d-1}}  + \ketbra{x_{d-1}}{x_1}.
\end{align}
The form of $B_1$ is important for the whole embedding argument to work in \cref{sec:main}.

The extended weighted CHSH test is added to make sure that the operator $X$ extracted from 
Alice and Bob's operator solution have eigenvalues $\omega_d$ and $\omega_d^{d-1}$.
In \cref{sec:main}, we will reason why showing these two eigenvalues is enough to guarantee that 
$U$ and $X$ has the eigen-structure required by \cref{lm:ux_independ}.
We denote this game that enforces the eigenvalues of the observable $X$ by
$\CHSH_X$, where the superscript $d$ emphasizes that the scoring rules of this game depend on $d$.

In this test, Alice and Bob each gets a question $x$,$y \in \{ 0, 1, \ast\}$ and 
they answer with $a,b \in \{0,1,\diamond,\perp\}$. 
Our self-test result follows the optimal correlation of this test.
Before presenting the optimal correlation, we give intuitions about how the players should behave.
\begin{itemize}
	\item \textbf{Case 1:} when $x = y = \ast$, Alice and Bob should answer with $a, b \in \{\diamond, \perp\}$ and 
	their answer should agree;
	\item \textbf{Case 2a:} when $x,y \in \{0,1\}$ and if they answer with $a,b \in \{0,1\}$, then
	their answers are scored according to $I_{\cot(-\pi/2d)}$;
	\item \textbf{Case 2b:} when $x,y \in \{0,1\}$ and if Alice answers with $\perp$, then all Bob's answers are irrelevant;
	\item \textbf{Case 3:} when $x \in {0,1}, y = \ast$, if Bob answers $\diamond$, 
	Alice should answer with $\{0.1\}$ but not $\perp$,
	if Bob answers $\perp$, Alice should answer $\perp$ too.
\end{itemize}
\textbf{The ideal strategy and ideal correlation}. Alice and Bob share the state $\ket{\psi} =\frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1} \ket{u_i}\ket{u_i}$.
We define two subspaces $V = \spn\{\ket{u_1}, \ket{u_{d-1}}\}$ and $V^\perp = \C^d \setminus\spn\{\ket{u_1}, \ket{u_{d-1}}\}$ and
define $\Pi_V$ and $\Pi_{V}^\perp$ to be the corresponding projectors. Note that $V$ is the subspace on which they should
maximize $\langle I_{\cot(-\pi/2d)} \rangle$.

@@

In the end, we determine the shared state.
The optimal correlation for $\CHSH_X$ uses state 
$\ket{\psi} = \frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1} \ket{u_i}\ket{u_i}$, 
so the shared state for $\G$ is $\frac{1}{2}( \ket{\psi}^{\oplus 4})$.
\end{proof}
Next we are going to prove that the strategy winning this game optimally can self-test $d-1$-dimensional EPR pair.

%-----------------------------------------------------------------
\subsection{Proof of \cref{thm:pr_2}}
%-----------------------------------------------------------------
\hl{This subsection needs to be formalized.}

>>>>

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{EPR^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\G}{G}
\newcommand{\LS}{LS}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}
\newcommand{\dr}[1]{d^{(#1)}}

@@

In summary, general $d$-dimensional maximally entangled states are self-tested by
modifying the correlation and enlarging the size of the correlation.
A natural question to ask is whether maximally entangled state with large local dimension
can be self-tested with fixed-sized correlation. 
An equivalent question to ask is whether it is possible to self-test maximally
entangled state more efficiently, with constant question and answer set. 
In this report, we give an affirmative answer to this question by proving the following theorem.
\begin{theorem}[Informal]
\label{thm:inf}
	There exists an infinite-sized set $D$ of odd prime numbers such that, for any $d \in D$, 
	the maximally entangled state of local dimension $d-1$ can be self-tested 
	with constant-sized question and answer alphabets.
\end{theorem}

The set $D$ is easily characterizable as it contains all the odd prime numbers with 
primitive root $2$, $3$ or $5$. It has been shown that there are infinitely many prime numbers
with primitive root in the set $\{2,3,5\}$ \cite{murty1988}, so the set $D$ has infinitely many elements.
To prove \cref{thm:inf}, we give explicit self-testing proof of 
the maximally entangled state with local dimension $d-1$ where the primitive root of $d$ is $2$ by explicitly giving the 
correlation that achieves this goal. Then the self-testing property of this correlation is 
given in the following theorem.
\begin{theorem}[Informal]
\label{thm:pr_2}
	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
	primitive root $2$, can be self-tested by a constant-sized correlation.
\end{theorem}
The correlation that we use to prove \cref{thm:pr_2} is denoted by $C(\dr{2})$.
We use the superscript $(2)$ to denote the primitive root of $d$.
Note that although the size of $C(\dr{2})$ does not depend on $d$, the optimal correlation does.
This correlation can be easily modified to self-test the maximally entangled state whose local dimension has 
primitive $3$ or $5$.

@@

\textbf{The weighted CHSH inequality \cite{acin2012}.}
The first building-block of our result is a robust self-testing result based on the weighted CHSH inequality.
In the CHSH scenario, Alice and Bob has binary observables $A_x,B_y$ for $x,y = 1,2$ 
on Hilbert space $\calH_A$ and $\calH_B$ respectively.
A binary observable is a Hermitian matrix whose eigenvalues are either $+1$ or $-1$.
The weighted CHSH inequality is given by 
\begin{align}
	\label{eq:chsh_op}
	\I_\alpha = \alpha\ip{A_1B_1}+\alpha\ip{A_1B_2} + \ip{A_2B_1} - \ip{A_2B_2}\leq 2\alpha,
\end{align}
where $\ip{A_xB_y}$ is the expectation value of of the observables.
If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, they cannot violate
the weighted CHSH inequality.
However, If they share entangled state $\ket{\psi}$, the maximal violation is 
\begin{align}
\label{eq:chsh_max}
 \I_\alpha \leq 2\sqrt{1+\alpha^2}.
\end{align}
\begin{definition}[Ideal strategy for $\I_\alpha$]
	\label{def:ideal}
	Define $\mu = \arctan(1/\alpha)$.
	The ideal strategy for weighted CHSH with parameter $\alpha$ (i.e. achieving maximal violation in \cref{eq:chsh_max})
	consists of the joint state $\ket{\EPR{2}}$ and observables $A_1 = \pauliz$, $A_2 = \paulix$,
	$B_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $B_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
\end{definition}
An interesting observation of the weighted CHSH inequality is that its maximal violation can certify the shared states and the 
measurements, which is the phenomenon of self-test. We give formal statement of this self-test result in \cref{sec:chsh}.

@@

%=======================================
\section{The linear system game}
\label{sec:lsg}
%=======================================
The goal of this section and the following two sections is to 
present a correlation that can self-test $\ket{\EPR{d-1}}$, 
where $d$ is prime and has primitive root $2$,
and this correlation is denoted by $C(\dr{2})$.
The correlation we constructed is the optimal correlation for a game $\G(\dr{2})$, which is the combination of two tests.
In this section, we introduce the linear system game which tests a relation that should be satisfied by 
Alice and Bob's observables.

Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$.
The main component of $\G(\dr{2})$ is a linear system game $\LS$, whose solution group is the embedding of the 
following group
\begin{align}
	\Pg= \langle u, x : uxu^{-1} = x^2 \rangle.
\end{align}
In other words, relations in the presentation of the solution group of $\LS$ can be combined to derive the
relation $uxu^{-1} = x^2$.
\begin{proposition}
	\label{prop:embed}
	The group $\Pg$ can be embedded into a linear system game $\LS$ over $\Z_2$,
	with $118$ variables and $91$ equations, where each equation involves $3$ variables.
\end{proposition}
The process of embedding $\Pg$ into the solution group of $\LS$ follows the recipe given in the proofs of
Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Slofstra's seminal work \cite{slofstra2017}.
The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}.
We give details of this embedding process in \cref{sec:power2}.

In the later parts of the paper, we use $n = 118$ and $m = 91$ to refer to the size of $\LS$.
The key feature of this embedding is that $\LS$ has constant-sized input-output alphabet
even if the generators $u$ and $x$ can have arbitrary order. 
The product of the generators $x_1$ and $x_2$ from the solution group of $\LS$ plays the role 
of the generator $x$ in $\Pg$ and the product of the generators $x_3$ and $x_4$ plays the role
of the generator $u$ in $\Pg$. As shown in \cref{sec:power2}, $x_1$,$x_2$,$x_3$ and $x_4$ satisfy the relation
\begin{align}
	(x_3x_4)(x_1x_2)(x_4x_3) = (x_1x_2)^2.
\end{align}
Hence the perfect quantum strategy $(\ket{\psi}, \{A_i, B_i\}_{i=1}^n)$ should satisfy 
the key relation that 
\begin{align}
	(A_3A_4) (A_1A_2)(A_4A_3) \ket{\psi} = (A_1A_2)^2\ket{\psi}, 
\end{align}
and similarly on Bob's side.
If we denote the unitary corresponding to the generator $u$ of $\Pg$ by $U$ and the unitary
corresponding to $x$ by $X$, then $U = A_3A_4$, $X= A_1A_2$, and 
$UXU\ct \ket{\psi} = X^2 \ket{\psi}$.
The special property of $U$ and $X$ is summarized in the following lemma.

\begin{lemma}
	\label{lm:ux_independ}
	Suppose there exist unitaries $U$ and $X$ which have the following forms
	\begin{align}
		X = \sum_{i=1}^{d-1} \omega_d^i \ketbra{i}{i} && U = \sum_{i=1}^{d-1}\ketbra{i/2}{i},
	\end{align}
	then the set $\{U^k X^l\}$ for $k=0,1\dots d-2$ and $l = 1,2\dots d-1$ forms a basis of 
	the ring of $(d-1)\times (d-1)$ matrices over $\C$.
\end{lemma}
Note that the unitaries $U$ and $X$ defined in the lemma above satisfy the condition $UXU^\dagger = X^2$.
In the self-test proof, this lemma will be a critical step.
\begin{proof}
We are going to show the $(d-1)^2$ matrices from the set $\{U^k X^l\}_{k \in[d-1], l \in [d-1]+1}$ are linearly independent.
Suppose there exists a set of complex numbers $\{ x_{k,l} \}_{k \in[d-1], l \in [d-1]+1}$
such that 
\begin{align}
	M = \sum_{k=0}^{d-2} \sum_{l=1}^{d-1} x_{k,l} U^k X^l = 0. 
\end{align}
We further assume that there exists a set of integers $\{ k_i \}_{i=1}^{d-1}$ such that $2^{k_i} \equiv i \pmod{d}$.
The fact that $2$ is a primitive root of $d$ guarantees that $k_i$'s are distinct.
Then we can group $\{x_{k,l}\}$ into vectors: $\ket{x_{k_1}}, \ket{x_{k_2}} \dots \ket{x_{k_{d-1}}}$,
where $\ket{x_{k_i}}= (x_{k_i, 1}, x_{k_i, 2} \dots x_{k_i, d-1})^\intercal$.
Our goal is equivalent to proving that $\ket{x_{k_i}} = 0$ for all $i$.

@@

%======================================
\section{The extended weighted CHSH test}
\label{sec:chsh}
%======================================
Before introducing the extended weighted CHSH test, we fill in some background about the weighted CHSH inequality,
namely, that its maximal violation can self-test $2$-dimensional EPR pair and rotated Pauli operators.
The robust self-testing result is summarized in the following theorem.
\begin{theorem}
\label{thm:selftest}
	Suppose the quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]+1}, \{\tilde{B}_y\}_{y \in [2]+1})$ achieves the violation
	at least $2\sqrt{1+\alpha^2} - \epsilon$
	for some $\epsilon$, then
	there exists a local isometry $\Phi = \Phi_A \x \Phi_B$ and an auxiliary state $\ket{aux}$  such that
	\begin{align}
		\| \Phi( \tilde{A}_x \x \tilde{B}_y \ket{\psi}) -\ket{junk} \x (A_x \x B_y) \ket{\EPR{2}}  \| = O((\alpha+\frac{1}{\alpha}) \sqrt{\epsilon})
	\end{align}
	for $x,y \in \{0, 1, 2\}$ where the subscript $0$ refers to the identity operator and $A_x, B_y$ are 
	defined in \cref{def:ideal}.
\end{theorem}
Our approach is very similar to the one used in Ref.~\cite{bamps2015} so we 
defer the proof of \cref{thm:selftest} till \cref{sec:selftest}.
After proving the robust self-testing result, we take one step further and observe an interesting property of the 
product of Bob's observables.
\begin{proposition}
\label{prop:2d-subspace}
	Let $\mu = \arctan(1/\alpha)$ for some $\alpha$.
	Suppose a quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]+1}, \{\tilde{B}_y\}_{y \in [2]+1})$ achieves the maximal 
	violation of  $\I_{\alpha}$, then $\tilde{B}_0\tilde{B}_1$ has eigenvalues $e^{i2\mu}$ and $e^{-i2\mu}$.
\end{proposition}
\begin{proof}[Proof of \cref{prop:2d-subspace}]
	Following the argument in the proof of \cref{thm:selftest} in \cref{sec:selftest}, we know
	$\tilde{Z}_B = (\tB_1+\tB_2)/2\cos(\mu)$ is a binary observable. \textcolor{red}{HF: Do we need to justify it?}
	Expanding $\tilde{Z}_B^2$ we get
	\begin{align*}
		\1 = \tilde{Z}_B^2 = \frac{\tB_1^2 + \tB_1\tB_2 + \tB_2\tB_1 + \tB_2^2}{4\cos(\mu)^2}
		=\frac{2\1 + \tB_1\tB_2 + \tB_2\tB_1}{4\cos^2(\mu)},
	\end{align*}
	so we can derive that 
	\begin{align}
	\label{eq:eig_v}
		\tB_1\tB_2 + \tB_2\tB_1 = 2(2\cos^2(\mu)-1)\1 = 2 \cos(2\mu) \1.
	\end{align}
	Observe that $(\tB_1\tB_2)^\dagger = \tB_2\tB_1$ and 
	$(\tB_2\tB_1)(\tB_1\tB_2) = \tB_2\1\tB_2 = \1$, then we can conclude that $\tB_1\tB_2$ is unitary.
	Suppose the eigen-decomposition of $\tB_1\tB_2$ is
	\begin{align}
		\tB_1\tB_2 = \sum_{i=1}^m \lambda_i \ketbra{i}{i}
	\end{align}
	for some orthonormal set of eigenvectors $\{ \ket{i} \}_{i=1}^m$
	and $\norm{\lambda_i} =1$ for $1 \leq i \leq m$.
	Eq.~\ref{eq:eig_v} tells us that for each $1 \leq i \leq m$
	\begin{align*}
		\lambda_i + \lambda_i^{-1} = 2\Re(\lambda_i) = 2 \cos(2\mu),
	\end{align*}
	so we can conclude that $\lambda_i = e^{i 2\mu}$ or $e^{-i 2\mu}$.

%	\begin{align}
%		\ket{\tpsi} = \sum_{i=1}^m \frac{c_i}{\sqrt{2}} (\ket{u_{i,0}}\ket{u_{i,0}}+\ket{u_{i,1}}\ket{u_{i,1}}),
%	\end{align}
%	where $c_i$'s are coefficients such that $\sum_{i=1}^m \norm{c_i}^2 = 1$.
%	The special property of the subspace $V_i = \spn( \ket{u_{i,0}}, \ket{u_{i,1}})$ is that 
%	\begin{align*}
%	(\tilde{B}_0 + \tilde{B}_1) \ket{u_{i,0}} = 2\cos(-\pi/2d) \ket{u_{i,0}} 
%	&&(\tilde{B}_0 + \tilde{B}_1) \ket{u_{i,1}} = -2\cos(-\pi/2d) \ket{u_{i,1}}\\
%	(\tilde{B}_0 - \tilde{B}_1) \ket{u_{i,0}} = 2\sin(-\pi/2d) \ket{u_{i,1}} 
%	&&(\tilde{B}_0 - \tilde{B}_1) \ket{u_{i,1}} = 2\sin(-\pi/2d) \ket{u_{i,0}}.
%	\end{align*}
%	It is straightforward to calculate that 
%	\begin{align*}
%		\tilde{B}_0\tilde{B}_1 \ket{u_{i,0}} = \cos(\pi/d) \ket{u_{i,0}} -\sin(\pi/d) \ket{u_{i,1}},&&
%		\tilde{B}_0\tilde{B}_1\ket{u_{i,1}} = \sin(\pi/d)\ket{u_{i,0}} + \cos(\pi/d) \ket{u_{i,1}},
%	\end{align*}
%	so we can conclude that 
%	\begin{align*}
%		&\tilde{B}_0\tilde{B}_1(\ket{u_{i,0}} + i\ket{u_{i,1}}) = e^{i \frac{\pi}{d}} (\ket{u_{i,0}} + i\ket{u_{i,1}}), &&
%		&\tilde{B}_0\tilde{B}_1(\ket{u_{i,0}} - i\ket{u_{i,1}}) = e^{-i \frac{\pi}{d}} (\ket{u_{i,0}} - i\ket{u_{i,1}}).
%	\end{align*}
%	Hence each $V_i$ is spanned by $\omega_d$-eigenvector and $\omega_d^{-1}$-eigenvector of $\tB_0\tB_1$.
\end{proof}

The extended weighted CHSH test is added to make sure that the operator $X$ extracted from 
Alice and Bob's operator solution of $\LS$ has eigenvalues $\omega_d$ and $\omega_d^{d-1}$.
In \cref{sec:main}, we will reason why showing these two eigenvalues is enough to guarantee that 
$U$ and $X$ has the eigen-structure required by \cref{lm:ux_independ}.
We denote this game that enforces the eigenvalues of the observable $X$ by
$\CHSH_X$, where the superscript $d$ emphasizes that the scoring rules of this game depend on $d$.

In this test, Alice and Bob each gets a question $x$,$y \in \{ 1, 2, \ast\}$ and 
they answer with $a,b \in \{0,1,\diamond,\perp\}$. 
The correlation $C(\dr{2})$ is the optimal correlation of this test.
Before presenting the optimal correlation, we give intuitions about how the players should behave.
\begin{itemize}
	\item \textbf{Case 1:} when $x = y = \ast$, Alice and Bob should answer with $a, b \in \{\diamond, \perp\}$ and 
	their answer should agree;
	\item \textbf{Case 2a:} when $x,y \in \{1,2\}$ and if they answer with $a,b \in \{0,1\}$, then
	their answers are scored according to $I_{\cot(-\pi/d)}$;
	\item \textbf{Case 2b:} when $x,y \in \{1,2\}$ and if Alice answers with $\perp$, then all Bob's answers are irrelevant;
	\item \textbf{Case 3:} when $x \in {1,2}, y = \ast$, if Bob answers $\diamond$, 
	Alice should answer with $\{0.1\}$ but not $\perp$,
	if Bob answers $\perp$, Alice should answer $\perp$ too.
\end{itemize}
\textbf{The ideal strategy and ideal correlation}. Alice and Bob share the state $\ket{\psi} =\frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1} \ket{u_i}\ket{u_i}$.
We define two subspaces $V = \spn\{\ket{u_1}, \ket{u_{d-1}}\}$ and $V^\perp = \C^d \setminus\spn\{\ket{u_1}, \ket{u_{d-1}}\}$ and
define $\Pi_V$ and $\Pi_{V}^\perp$ to be the corresponding projectors. Note that $V$ is the subspace on which they should
maximize $\langle I_{\cot(-\pi/d)} \rangle$.

@@

In the end, we determine the shared state.
The optimal correlation for $\CHSH_X$ uses state 
$\ket{\psi} = \frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1} \ket{u_i}\ket{u_i}$, 
so the shared state for $\G$ is $\frac{1}{2}( \ket{\psi}^{\oplus 4})$.
\end{proof}
Next we are going to prove that the correlation $C(\dr{2})$ that is produced by the 
strategy winning this game optimally, can self-test $d-1$-dimensional EPR pair.
